Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-17 article/article.tex
Commit 2024-05-17 11:12

The above clear sky reference values are not enough to describe the long
term variation due to the changes of the atmospheric constituents. As
observed by \citet{Natsis2023}, there is long term brightening effect,
over Thessaloniki for the studied period. In order to better describe
this change, we used, estimations of AOD change derived from two
sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
\(-3.8\,\%\) per year at AOD on \(340\) nm, using a Brewer
spectrophotometer. For 2005 to 2023, we derived the trend from the
available AERONET data.

To create a unified trend for the long term change of the clear sky
irradiance, we sim simulated

>>>>

The above clear sky reference values are not enough to describe the long
term variation due to the changes of the atmospheric constituents. As
observed by \citet{Natsis2023}, there is long term brightening effect,
over Thessaloniki for the studied period. In order to better describe
this change, we used, estimations of AOD change derived from two
sources. For 1993 -- 2005, \citet{Kazadzis2007} have found a change of
\(-3.8\,\%\) per year at AOD on \(340\,\text{nm}\), using a Brewer
spectrophotometer. For 2005 to 2023, we derived the trend from the
available AERONET data.

To create a unified trend for the long term change of the clear sky
irradiance, we simulated the values of AOD derived from those sources
with Libradtran. For both, we use the AOD at \(500\,\text{nm}\), which
was inferred by the available Ångström exponent, and we choose the SZA
of \(55^\circ\) as a representative value for all runs.

For the period 1993 -- 2005

For the period 2005 -- 2005 we used
